---
title: "env_data"
author: "allyson_demerlis"
date: "2024-10-16"
output: html_document
---
# load libraries
```{r}
library(tidyverse)
```

# import and tidy CCC temp logger (tilt meter)
```{r}
cures_frame_tilt_temp <- read_excel("raw_data/Oct2020_Jan2022_1901102_urban-2020-10_(0)_Temperature.xlsx", sheet = "1901102_urban-2020-10_(0)_Tempe")
#logged every 15 min

#edit cures frame time
cures_frame_tilt_temp$Datetime <- as.POSIXct(cures_frame_tilt_temp$Datetime, tz="UTC")
cures_frame_tilt_temp$Datetime_EST <- with_tz(cures_frame_tilt_temp$Datetime, "America/New_York")

# Filter the data to select time points at 2-hour intervals
cures_frame_tilt_temp <- cures_frame_tilt_temp %>%
  filter(minute(Datetime_EST) == 0 & (hour(Datetime_EST) %% 2 == 0))

#add cures frame site
cures_frame_tilt_temp %>% 
  mutate(site = "CCC") %>% 
  dplyr::select(!Date:Datetime) %>% 
  dplyr::rename(Temperature = `Temperature (C)`) -> cures_frame_tilt_temp

max(cures_frame_tilt_temp$Datetime_EST) #"2022-02-01 12:00:00 EST"
min(cures_frame_tilt_temp$Datetime_EST) #"2020-10-12 20:00:00 EDT"
```

plot all data to visualize
```{r}
ggplot(cures_frame_tilt_temp, aes(x=Datetime_EST, y=Temperature)) +
  geom_point()
```

```{r}
cures_frame_tilt_temp %>% 
  filter(as.Date(Datetime_EST) < "2020-11-01") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature)) +
  geom_point()

# remove first day of data because the range is not real

cures_frame_tilt_temp %>% 
  filter(as.Date(Datetime_EST) > "2020-10-13") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature)) +
  geom_point()

cures_frame_tilt_temp %>% 
  filter(as.Date(Datetime_EST) > "2020-10-13") -> CCC_temp_filtered
```


```{r}
CCC_temp_filtered %>% 
  filter(as.Date(Datetime_EST) < "2020-12-06" & as.Date(Datetime_EST) > "2020-12-03") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point(alpha = 0.7) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#december 4 2020 looks concerning
```

```{r}
CCC_temp_filtered %>% 
  filter(as.Date(Datetime_EST) < "2020-12-06" & as.Date(Datetime_EST) > "2020-12-03") %>% 
  filter(Temperature > 21 & Temperature < 25) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point(alpha = 0.7) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

CCC_temp_filtered %>% 
  filter(as.Date(Datetime_EST) < "2020-12-06" & as.Date(Datetime_EST) > "2020-12-03") %>% 
  filter(Temperature > 21 & Temperature < 25) -> dec2020_CCCfiltered
```


calculate daily thermal variability during entire dataset
```{r}
CCC_temp_filtered %>% 
  filter(!as.Date(Datetime_EST) < "2020-12-06" & as.Date(Datetime_EST) > "2020-12-03") %>%  
  full_join(., dec2020_CCCfiltered) %>% 
  group_by(as.Date(Datetime_EST)) %>% 
  summarise(mean_daily_temp = mean(Temperature), sd_daily_temp = sd(Temperature), daily_range = (max(Temperature)-min(Temperature))) %>% 
  ggplot(., aes(x=`as.Date(Datetime_EST)`, y=daily_range)) +
  geom_line() +
  theme_bw() 

# lots of outliers after Dec 2021 but we don't need that data
```

## overwriting CCC filtered datafile
```{r}
CCC_temp_filtered %>% 
  filter(!as.Date(Datetime_EST) < "2020-12-06" & as.Date(Datetime_EST) > "2020-12-03") %>%  
  full_join(., dec2020_CCCfiltered) -> CCC_temp_filtered
```



filter for experimental period (June to December 2021)
```{r}
CCC_temp_filtered %>% 
  filter(as.Date(Datetime_EST) < "2021-12-01" & as.Date(Datetime_EST) > "2021-06-23") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point(alpha = 0.7) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

calculate daily thermal variability during experimental period
```{r}
CCC_temp_filtered %>% 
  filter(as.Date(Datetime_EST) < "2021-12-01" & as.Date(Datetime_EST) > "2021-06-23") %>% 
  group_by(as.Date(Datetime_EST)) %>% 
  summarise(mean_daily_temp = mean(Temperature), sd_daily_temp = sd(Temperature), daily_range = (max(Temperature)-min(Temperature))) %>% 
  ggplot(., aes(x=`as.Date(Datetime_EST)`, y=daily_range)) +
  geom_line() +
  theme_bw() 
```

# import and tidy KB Nursery HOBO logger

We want to plot all available data to illustrate what the temperature profiles were like for all corals before the transplantation to the CCC site occurred.
```{r}
#HOBO logs every two hours
convertFtoC <- function(F) {
  C <- (F - 32) * 5/9
  return(C)
}

KB_01092018<-read_csv("raw_data/KBNursery_2018_01_09.csv", skip = 1)
KB_01092018  %>% 
  dplyr::select(!`#`) %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-05:00`, tz = "Etc/GMT+5"), tzone = "Etc/GMT+5")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °F (LGR S/N: 20194578, SEN S/N: 20194578)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20194578, SEN S/N: 20194578)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) %>% 
  mutate(Temperature=convertFtoC(Temperature)) -> KB_01092018

KB_07092019<-read_csv("raw_data/KBNursery_2019_07_09.csv", skip = 1)
KB_07092019  %>% 
  dplyr::select(!`#`) %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 10795158, SEN S/N: 10795158)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 10795158, SEN S/N: 10795158)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_07092019

KB_10152019<-read_csv("raw_data/KBNursery_2019_10_15.csv", skip = 1)
KB_10152019 %>% 
  dplyr::select(!`#`) %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20518526, SEN S/N: 20518526)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20518526, SEN S/N: 20518526)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_10152019

KB_01162020<-read_csv("raw_data/KBNursery_2020_01_16.csv", skip = 1)
KB_01162020 %>% 
  dplyr::select(!`#`) %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-05:00`, tz = "Etc/GMT+5"), tzone = "Etc/GMT+5")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20473194, SEN S/N: 20473194)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20473194, SEN S/N: 20473194)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_01162020

KB_03062020<-read_csv("raw_data/KBNursery_2020_03_06.csv", skip = 1)
KB_03062020 %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-05:00`, tz = "Etc/GMT+5"), tzone = "Etc/GMT+5")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20685544, SEN S/N: 20685544)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20685544, SEN S/N: 20685544)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_03062020

KB_05012020<-read_csv("raw_data/KBNursery_2020_05_01.csv", skip = 1)
KB_05012020 %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20685559, SEN S/N: 20685559)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20685559, SEN S/N: 20685559)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_05012020

KB_09112020<-read_csv("raw_data/KBNursery_2020_09_11.csv", skip = 1)

KB_09112020 %>% 
  mutate(Datetime_EST=with_tz(mdy_hm(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20597589, SEN S/N: 20597589)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20597589, SEN S/N: 20597589)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_09112020

KB_02102021 <- read_csv("raw_data/KBNursery_2021_02_10.csv", skip = 1)
KB_02102021 %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-05:00`, tz = "Etc/GMT+5"), tzone = "Etc/GMT+5")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20976501, SEN S/N: 20976501)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20976501, SEN S/N: 20976501)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_02102021

KB_05282021 <- read_csv("raw_data/KBNursery_2021_05_28.csv", skip = 1)
KB_05282021 %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 21085862, SEN S/N: 21085862)`) %>% 
  dplyr::select(Temperature, Datetime_EST) %>% 
  mutate(Light = NA) -> KB_05282021

KB_08112021 <- read_csv("raw_data/KBNursery_2021_08_11.csv", skip = 1)
KB_08112021 %>% 
  mutate(Datetime_EST=with_tz(mdy_hm(`Date Time, GMT-04:00`, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 20831178, SEN S/N: 20831178)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 20831178, SEN S/N: 20831178)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_08112021

KB_120821 <- read_csv("raw_data/KBNursery_2021_12_08.csv", skip = 1)
KB_120821%>% 
  mutate(Datetime_EST=with_tz(mdy_hm(`Date Time, GMT-05:00`, tz = "Etc/GMT+5"), tzone = "Etc/GMT+5")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  dplyr::rename(Temperature = `Temp, °C (LGR S/N: 21236769, SEN S/N: 21236769)`) %>% 
  dplyr::rename(Light = `Intensity, lum/ft² (LGR S/N: 21236769, SEN S/N: 21236769)`) %>% 
  dplyr::select(Temperature, Light, Datetime_EST) -> KB_120821

rbind(KB_01092018, KB_07092019, KB_10152019, KB_01162020, KB_03062020, KB_05012020, KB_09112020, KB_02102021, KB_05282021, KB_08112021, KB_120821) -> all_KB_data

all_KB_data %>% 
  mutate(site = "Nursery") -> all_KB_data

all_KB_data$Temperature <- as.numeric(all_KB_data$Temperature)
```

plot all raw data 
```{r}
ggplot(all_KB_data, aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %Y",  # Customize the date format
                     date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

```{r}
all_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-07-08" & as.Date(Datetime_EST) < "2021-12-01") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %Y",  # Customize the date format
                     date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```


plot raw data within experimental period
```{r}
all_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2021-06-23" & as.Date(Datetime_EST) < "2021-12-01") %>%
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw() +
  scale_x_datetime(date_labels = "%b %Y",  # Customize the date format
                     date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
```

## outlier removal
```{r}
# Z-score method
all_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-07-10" & as.Date(Datetime_EST) < "2021-12-01") %>%
  mutate(z_score = scale(Temperature)) %>% 
  filter(abs(z_score) < 3) -> filtered_KB_data

ggplot(filtered_KB_data, aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
#still a lot of outliers
```

```{r}
# separate by year and visually inspect each section

#2019
filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) < "2019-12-31") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-10-12" & as.Date(Datetime_EST) < "2019-10-20") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-10-12" & as.Date(Datetime_EST) < "2019-10-20") %>% 
  filter(Temperature < 31.5 & Temperature > 28) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
#looks better

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-10-12" & as.Date(Datetime_EST) < "2019-10-20") %>% 
  filter(Temperature < 31.5 & Temperature > 28) -> oct2019_filtered_data

# 2020
filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2019-12-31" & as.Date(Datetime_EST) < "2020-12-31") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

#three spots of concern: january, after april, and before october
filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-01-05" & as.Date(Datetime_EST) < "2020-01-31") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-01-05" & as.Date(Datetime_EST) < "2020-01-31") %>% 
  filter(Temperature > 23 & Temperature < 27) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-01-05" & as.Date(Datetime_EST) < "2020-01-31") %>% 
  filter(Temperature > 23 & Temperature < 27) -> jan2020_filtered

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-03-01" & as.Date(Datetime_EST) < "2020-03-15") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
#filter temp < 27

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-03-01" & as.Date(Datetime_EST) < "2020-03-15") %>% 
  filter(Temperature < 27) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-03-01" & as.Date(Datetime_EST) < "2020-03-15") %>% 
  filter(Temperature < 27) -> mar2020_filtered

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-04-05" & as.Date(Datetime_EST) < "2020-06-01") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
# filtering temps less than 25ºC should get rid of it

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-04-05" & as.Date(Datetime_EST) < "2020-06-01") %>% 
  filter(Temperature > 25) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
# looks good

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-04-05" & as.Date(Datetime_EST) < "2020-06-01") %>% 
  filter(Temperature > 25) -> may2020_filtereddata

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-09-01" & as.Date(Datetime_EST) < "2020-09-15") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
# filter anything less than 29ºC and greater than 31.5

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-09-01" & as.Date(Datetime_EST) < "2020-09-15") %>% 
  filter(Temperature > 29 & Temperature < 31.5) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2020-09-01" & as.Date(Datetime_EST) < "2020-09-15") %>% 
  filter(Temperature > 29 & Temperature < 31.5) -> sept2020_filtereddata

#2021
filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2021-01-01" & as.Date(Datetime_EST) < "2021-12-31") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
# two areas -- june and august

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2021-05-25" & as.Date(Datetime_EST) < "2021-06-15") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
#remove temps less than 25

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2021-05-25" & as.Date(Datetime_EST) < "2021-06-15") %>%
  filter(Temperature > 25) -> june2021_filtered

filtered_KB_data %>% 
  filter(as.Date(Datetime_EST) > "2021-08-10" & as.Date(Datetime_EST) < "2021-08-24") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  theme_bw()
# the temperature is oscillating 5 degrees per day 

# for this section, I am going to manually filter out the low temps <27ºC and extremely high temps
filtered_KB_data %>% 
  dplyr::select(!z_score) %>% 
  filter(as.Date(Datetime_EST) > "2021-08-10" & as.Date(Datetime_EST) < "2021-08-24") %>% #301 
  filter(Temperature > 27 & Temperature < 31.5) -> august_filtered_KB_data

# all time
filtered_KB_data %>% 
  filter(!(as.Date(Datetime_EST) > "2019-10-12" & as.Date(Datetime_EST) < "2019-10-20")) %>% 
  full_join(., oct2019_filtered_data) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-01-05" & as.Date(Datetime_EST) < "2020-01-31")) %>% 
  full_join(., jan2020_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-03-01" & as.Date(Datetime_EST) < "2020-03-15")) %>%
  full_join(., mar2020_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-04-05" & as.Date(Datetime_EST) < "2020-06-01")) %>% 
  full_join(., may2020_filtereddata) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-09-01" & as.Date(Datetime_EST) < "2020-09-15")) %>% 
  full_join(., sept2020_filtereddata) %>% 
  filter(!(as.Date(Datetime_EST) > "2021-05-25" & as.Date(Datetime_EST) < "2021-06-15")) %>% 
  full_join(., june2021_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2021-08-10" & as.Date(Datetime_EST) < "2021-08-24")) %>% 
  full_join(., august_filtered_KB_data) %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  geom_line() +
  theme_bw() 

filtered_KB_data %>% 
  filter(!(as.Date(Datetime_EST) > "2019-10-12" & as.Date(Datetime_EST) < "2019-10-20")) %>% 
  full_join(., oct2019_filtered_data) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-01-05" & as.Date(Datetime_EST) < "2020-01-31")) %>% 
  full_join(., jan2020_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-03-01" & as.Date(Datetime_EST) < "2020-03-15")) %>%
  full_join(., mar2020_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-04-05" & as.Date(Datetime_EST) < "2020-06-01")) %>% 
  full_join(., may2020_filtereddata) %>% 
  filter(!(as.Date(Datetime_EST) > "2020-09-01" & as.Date(Datetime_EST) < "2020-09-15")) %>% 
  full_join(., sept2020_filtereddata) %>% 
  filter(!(as.Date(Datetime_EST) > "2021-05-25" & as.Date(Datetime_EST) < "2021-06-15")) %>% 
  full_join(., june2021_filtered) %>% 
  filter(!(as.Date(Datetime_EST) > "2021-08-10" & as.Date(Datetime_EST) < "2021-08-24")) %>% 
  full_join(., august_filtered_KB_data)  -> tidy_KB_data

# experimental period
filtered_KB_data %>% 
  filter(!(as.Date(Datetime_EST) > "2021-08-10" & as.Date(Datetime_EST) < "2021-08-24")) %>% 
  full_join(., august_filtered_KB_data) %>% 
  filter(as.Date(Datetime_EST) < "2021-12-01" & as.Date(Datetime_EST) > "2021-06-20") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_point() +
  geom_line() +
  theme_bw() 
```

calculate daily thermal variability
```{r}
tidy_KB_data %>% 
  group_by(as.Date(Datetime_EST)) %>% 
  summarise(mean_daily_temp = mean(Temperature), sd_daily_temp = sd(Temperature), daily_range = (max(Temperature)-min(Temperature))) %>% 
  ggplot(., aes(x=`as.Date(Datetime_EST)`, y=daily_range)) +
  geom_line() +
  theme_bw() 
```

# join both datasets and plot temps 
```{r}
tidy_KB_data %>% 
  full_join(., CCC_temp_filtered) %>% 
  filter(as.Date(Datetime_EST) < "2021-12-01") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_line() +
  theme_bw() +
  labs(x="Date", y = "Temp (ºC)") +
  scale_color_manual(values = c("CCC" = "orange", "Nursery" = "darkblue")) +
  scale_x_datetime(date_labels = "%b %Y",  # Customize the date format
                     date_breaks = "3 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_vline(xintercept=as.POSIXct(as.Date("2021-06-23")))
#ggsave("CCCvsnursery_temp.png", width=10, height = 7)
```

# save tidied dataset

```{r}
tidy_KB_data %>% 
  full_join(., CCC_temp_filtered) %>% 
  select(Temperature, Datetime_EST, site) %>% 
  as.data.frame() %>% 
  write_csv(., "tidy_KB_CCC_data.csv")
```


# plot CCC HOBO data to show why it was removed
```{r}
CCC_hobo <- read_csv("raw_data/CCC_HOBO.csv", skip = 1)

convertFtoC <- function(F) {
  C <- (F - 32) * 5/9
  return(C)
}

CCC_hobo %>% 
  rename(Temperature = `Temp, °F (LGR S/N: 20261765, SEN S/N: 20261765)`) %>% 
  rename(Date_GMT = `Date Time, GMT-04:00`) %>% 
  select(Date_GMT, Temperature) %>% 
  mutate(site = "CCC_HOBO") %>% 
  mutate(Datetime_EST=with_tz(mdy_hms(Date_GMT, tz = "Etc/GMT+4"), tzone = "Etc/GMT+4")) %>% 
  mutate(Datetime_EST=with_tz(Datetime_EST, tzone = "America/New_York")) %>% 
  mutate(Temperature=convertFtoC(Temperature)) -> CCC_hobo
```


## virginia key buoy water temp data
```{r}
file_paths <- c("raw_data/virginiakeybuoy/vakf1h2020.txt", "raw_data/virginiakeybuoy/vakf1h2021.txt", "raw_data/virginiakeybuoy/vakf1h2022.txt")

process_file <- function(file_path) {
  data <- read.table(file_path, header = FALSE, sep = "", comment.char = "#", stringsAsFactors = FALSE)

# Read the first two lines to get the column names
lines <- read_lines(file_path, n_max = 2)

# Extract column names from the second line
column_names <- strsplit(lines[1], "\\s+")[[1]]

# Assign the column names to the data frame
colnames(data) <- column_names

data %>% 
  rename(Temperature = WTMP) %>% 
  select(`#YY`:mm,Temperature) -> data
  
data$Datetime <- ymd_hm(paste(data$`#YY`, data$MM, data$DD, data$hh, data$mm))

data$Datetime <- as.POSIXct(data$Datetime, tz="UTC")
data$Datetime_EST <- with_tz(data$Datetime, "America/New_York")

return(data)
}

# Initialize an empty list to store the processed data frames
all_data <- list()

# Loop over the file paths and process each file
for (file_path in file_paths) {
  data <- process_file(file_path)
  all_data[[file_path]] <- data
}

# Optionally, combine all data frames into one, if needed
combined_data <- do.call(rbind, all_data)

# View the combined data
print(combined_data)

combined_data %>% 
  select(Temperature, Datetime_EST) %>% 
  mutate(site = "VK_Buoy") -> vkbuoydata

rownames(vkbuoydata) <- NULL

#VK_Buoy data gets written as "999" if there is no available data for that time point, so filter that out

vkbuoydata %>% 
  filter(Temperature < 999) -> vkbuoydata

# Filter the data to select time points at 2-hour intervals
vkbuoydata <- vkbuoydata %>%
  filter(minute(Datetime_EST) == 0 & (hour(Datetime_EST) %% 2 == 0))
```

```{r}
tidy_KB_data <- read_csv("tidy_KB_CCC_data.csv")
```


```{r}
tidy_KB_data #every 2 hr

vkbuoydata %>% 
  select(Temperature, Datetime_EST) %>% 
  mutate(site = "VK Buoy") -> vkbuoydata_subset #every 2 hr

full_join(CCC_hobo, tidy_KB_data) %>% 
  full_join(., vkbuoydata_subset) %>% 
  select(!Date_GMT) %>% 
  filter(as.Date(Datetime_EST) < "2021-12-01" & as.Date(Datetime_EST) > "2021-06-20") %>% 
  ggplot(., aes(x=Datetime_EST, y=Temperature, color = site)) +
  geom_line() +
  theme_classic() +
  labs(x="Date") 
#ggsave("plot_withCCCHOBO.png")
```


